---
title: "2020 & 2024 election studies: data, exclusions and descriptive results"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
params:
  # Which session set the main figures use. One of the sets defined in the
  # "Session sets" section: "main", "comprehension", "strict_timing",
  # "high_attention", "no_us_exclusion", "task_first", "original". The robustness section
  # shows all of them.
  main_set: "main"
  # RT window (ms): the word-level filter for the RT plots, and what counts
  # as "too fast" / "too slow" in the exclusions.
  rt_min: 180
  rt_max: 5000
  # Default exclusion: drop reading sessions with more than this many
  # critical-trial words under rt_min.
  max_words_too_fast: 2
  # Default exclusion: drop Maze/mazerace sessions whose proportion of
  # critical-trial words chosen correctly on the first try is below this.
  maze_accuracy_min: 0.8
  # RT plots: keep only Maze words chosen correctly on the first try.
  maze_correct_only: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 4)
library(tidyverse)
library(here)
library(knitr)
library(kableExtra)

theme_set(theme_bw())
dodge <- position_dodge(width = .2)

# One colour per level, used in every figure.
pronoun_colors <- c(she = "#D95F02", he = "#1B9E77", they = "#7570B3")
pronoun_scale <- scale_color_manual(values = pronoun_colors, breaks = names(pronoun_colors))
# Recall answers use the matching pronoun colours (female candidate = she, ...).
recall_colors <- c("Kamala Harris" = "#D95F02", "Mike Pence" = "#1B9E77", "Donald Trump" = "#1B9E77",
                   "Writer is unsure" = "#7570B3", "I don't remember" = "grey60")
# Data loading, exclusions and session sets, shared with analysis/models/.
source(here("analysis", "analysis_data.R"))
stopifnot(params$main_set %in% set_levels)

# Points are means, error bars bootstrapped 95% CIs, lines connect means.
line_with_errorbars <- function(dodge = position_dodge(width = .2)) {
  list(
    stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", position = dodge),
    stat_summary(fun = "mean", geom = "line", position = dodge)
  )
}

show_table <- function(df, caption = NULL) {
  kable(df, caption = caption, format.args = list(big.mark = ",")) |>
    kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE)
}
```

This document is generated from the processed data in this repo
(`combined/` plus each study's `processed/` tables; see `DATA.md`). The main
figures use the **`r params$main_set`** session set (defined under
*Session sets*), a word-level RT window of
**`r params$rt_min`–`r params$rt_max` ms**, and Maze correct-first-try only =
**`r params$maze_correct_only`**. These are `params` in the YAML header, so
the same document can be re-rendered under other choices:

```
rmarkdown::render("analysis/descriptives.Rmd", params = list(main_set = "comprehension"))
```


```{r load}
analysis_data <- load_analysis_data(list(
  rt_min = params$rt_min, rt_max = params$rt_max,
  max_words_too_fast = params$max_words_too_fast, maze_accuracy_min = params$maze_accuracy_min
))
sessions <- analysis_data$sessions
cloze <- analysis_data$cloze
reading <- analysis_data$reading
critical_words <- analysis_data$critical_words
recall <- analysis_data$recall
step_cols <- analysis_data$step_cols
participant_steps <- analysis_data$participant_steps
session_sets <- analysis_data$session_sets
expectation_sets <- analysis_data$expectation_sets
kept_sessions <- session_sets[[params$main_set]]
```

# Data

Two between-participant experiments around the 2020 (Harris for vice
president) and 2024 (Harris for president) US elections. Each session gives
event-expectation sliders plus **one** critical trial of one task (cloze,
A-Maze, SPR, or the 2020-only mazerace control), in a random order, before
(pre) or after (post) the election. `OVERVIEW.md` has the design side by
side; `METHODS-SUMMARY.md` has sourced detail.

```{r sessions-table}
sessions |>
  count(study, task, round) |>
  pivot_wider(names_from = round, values_from = n) |>
  show_table("All sessions (before exclusions) by study, task and round")
```

# Exclusions

## Default exclusions

Decided 2026-10-07 (from the candidate counts further down). Applied
identically to both studies, in this order; each column counts sessions
newly removed by that step.

Participant-wide (all tasks and the event sliders):

1. **Incomplete**: 2024 runs without the end-of-study survey (2020 Ibex
   logs only contain submitted sessions).
2. **Repeat participant**: 2020: same IP pseudonym or MTurk worker as an
   earlier session in the round, or the worker took part pre-election
   (`excl_repeat_ip`, `excl_repeat_worker`, `excl_worker_in_pre_round`);
   2024: same `workerid` submitted twice, or removed by the original's
   Prolific-ID check.
3. **Not a native English speaker** (self-report).
4. **Not a US citizen or not a US resident** (self-report). The original
   2020 pipeline did not apply this; 2024's did.

Reading tasks only (Maze, SPR, mazerace), counted over the critical
trial: the context sentence and both critical sentences (the practice item
is not used).

5. **No critical trial**: a few 2024 reading sessions never completed the
   critical trial (all already excluded by the original pipeline).
6. **More than `r params$max_words_too_fast` words too fast** (RT under
   `r params$rt_min` ms).
7. **Maze accuracy below `r params$maze_accuracy_min`** (Maze and
   mazerace): proportion of words chosen correctly on the first try.

Cloze only:

8. **Nonsense completion** (`cloze_nonsense`; see `DATA.md`): blank, only
   "yes"/"no"/a number, a pasted ID, text copied from the context
   sentence, or a single word that doesn't continue the sentence.

Event expectations: every step above applies to the sliders too,
including the task-quality steps 5–8. A session that failed its task's
quality check is treated as an inattentive or not-good-faith participant,
so their slider answers are dropped along with their task data (2020
sessions failing these checks put far more on "someone else"). In
addition, sessions with **all sliders at 0** have undefined probabilities
and are left out of the expectation figures; their task data is kept.

**Bots** have no direct signal: 2020's bot-screening question had the same
value in every session, and 2024 had none. Steps 6 and 7 are the proxies
for reading tasks, and step 8 for cloze.

```{r default-exclusions}
# The steps themselves are defined in analysis/analysis_data.R.
# Sequential: count each session at the first step that removes it.
first_step <- sessions |>
  select(study, round, task, session_id, all_of(step_cols)) |>
  pivot_longer(all_of(step_cols), names_to = "step", values_to = "flag") |>
  filter(flag) |>
  slice_min(step, by = session_id) |>
  count(study, round, task, step) |>
  pivot_wider(names_from = step, values_from = n, values_fill = 0)
sequential <- sessions |>
  count(study, round, task, name = "all_sessions") |>
  left_join(first_step, by = c("study", "round", "task")) |>
  left_join(count(filter(sessions, !excl_main), study, round, task, name = "kept"),
            by = c("study", "round", "task")) |>
  mutate(across(where(is.numeric), \(x) coalesce(x, 0L)))
for (step in setdiff(step_cols, names(sequential))) sequential[[step]] <- 0L
sequential <- select(sequential, study, task, round, all_sessions, all_of(step_cols), kept)
stopifnot(all(sequential$all_sessions - rowSums(select(sequential, all_of(step_cols))) == sequential$kept))
sequential |>
  mutate(round = factor(round, levels = round_levels)) |>
  arrange(study, task, round) |>
  show_table("Default exclusions, applied in order (sessions removed at each step)")
```

## Comprehension accuracy

One comprehension question followed each critical Maze, SPR and mazerace
trial. The 2020 code defines a question for each critical sentence, but
the logs hold exactly one per session, and in every 2020 Maze/SPR session
it is the question about **sentence 1** (checked against the stimulus
file). Neither 2020 pipeline used the answers; 2024's required a correct
answer for Maze and SPR. Here it is a robustness set, not a default
exclusion.

```{r comprehension}
comprehension_sessions <- sessions |>
  filter(is_reading, !excl_main)
comprehension_sessions |>
  group_by(study, task, round) |>
  summarize(n = n(), no_answer = sum(comprehension_n == 0),
            prop_correct = round(mean(comprehension_correct), 2), .groups = "drop") |>
  pivot_wider(names_from = round, values_from = c(n, no_answer, prop_correct)) |>
  show_table("Comprehension accuracy (sessions kept by the default exclusions; no answer counts as incorrect)")
```

```{r comprehension-by-condition, fig.height = 3.5}
comprehension_sessions |>
  filter(task %in% c("maze", "spr")) |>
  inner_join(distinct(critical_words, session_id, pro1_type), by = "session_id", relationship = "one-to-one") |>
  ggplot(aes(x = round, y = as.numeric(comprehension_correct), color = pro1_type, group = pro1_type)) +
  line_with_errorbars(dodge) +
  facet_wrap(~ paste(study, task), nrow = 1) +
  pronoun_scale +
  labs(x = NULL, y = "Proportion correct", color = "Pronoun 1",
       title = "Comprehension accuracy by condition (default exclusions)")+
  coord_cartesian(ylim=c(0,1))+geom_hline(aes(yintercept=.5),lty="dashed")
```

## Maze accuracy

Each session's accuracy is the proportion of its critical-trial Maze words
chosen correctly on the first try. Chance is 0.5. Shown for
sessions that pass the participant-wide steps (1–4), before the
reading-task steps.

```{r maze-accuracy-hist, fig.height = 3.5}
sessions |>
  filter(is_maze, !excl_participant, !step_5_no_critical_trial) |>
  ggplot(aes(x = maze_accuracy)) +
  geom_histogram(binwidth = .05, boundary = 0) +
  geom_vline(xintercept = params$maze_accuracy_min, linetype = "dashed") +
  facet_grid(round ~ paste(study, task), scales = "free_y") +
  labs(x = "Proportion of words correct on the first try", y = "Sessions",
       title = "Per-session Maze accuracy (dashed line = default threshold)")
```

## RT plausibility

How many of each session's critical-trial words fall outside
`r params$rt_min`–`r params$rt_max` ms? Is it close to all-or-nothing per
session, or are there many borderline sessions with a few out-of-window
words? A critical trial has about 70 words in 2020 Maze and SPR, 36 in
mazerace, and about 49 in 2024. Shown for
sessions that pass the participant-wide steps (1–4).

```{r rt-window-distribution-data}
rt_direction_counts <- sessions |>
  filter(is_reading, !excl_participant, !step_5_no_critical_trial) |>
  select(study, round, task, session_id, words, too_fast = n_too_fast, too_slow = n_too_slow) |>
  pivot_longer(c(too_fast, too_slow), names_to = "direction", values_to = "n_words") |>
  mutate(direction = recode(direction,
                            too_fast = paste0("too fast (< ", params$rt_min, " ms)"),
                            too_slow = paste0("too slow (> ", params$rt_max, " ms)")),
         prop_words = n_words / words,
         panel = paste(study, task))
count_bins <- c("0", "1", "2", "3–5", "6–10", "11–20", "> 20")
rt_direction_counts <- rt_direction_counts |>
  mutate(n_words_bin = cut(n_words, breaks = c(-Inf, 0, 1, 2, 5, 10, 20, Inf), labels = count_bins))
stopifnot(!anyNA(rt_direction_counts$n_words_bin))
```

```{r rt-window-count-bins, fig.height = 5, fig.width = 10}
ggplot(rt_direction_counts, aes(x = round, fill = n_words_bin)) +
  geom_bar(position = "fill") +
  facet_grid(direction ~ panel) +
  scale_fill_viridis_d(option = "magma", direction = -1, end = .9) +
  labs(x = NULL, y = "Proportion of sessions", fill = "Words outside\nthe window",
       title = "Sessions by number of words outside the RT window")
```

The same counts as a proportion of each session's words, for sessions with
at least one such word (the bar chart above shows how many have none):

```{r rt-window-prop-hist, fig.height = 7, fig.width = 10}
ggplot(filter(rt_direction_counts, n_words > 0), aes(x = prop_words, fill = round)) +
  geom_histogram(binwidth = .05, boundary = 0, position = "identity", alpha = .5) +
  facet_grid(panel ~ direction, scales = "free_y") +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "Proportion of the session's words", y = "Sessions", fill = NULL,
       title = "Sessions with at least one word outside the RT window")
```

**2020 data quality.** Before any exclusions, 2020 has many sessions that
click through fast: Maze accuracy near chance (0.5) with very short
first-click RTs, and SPR words read in under `r params$rt_min` ms. These
are much more common post-election. This looks like fast clicking, not a
processing artefact: errors are equally common for left and right answers,
and the same pattern holds on the practice item. The repeat-participant
step removes most of these sessions; steps 6 and 7 remove the near-chance
and fast-clicking group that remains. Fast clicking is close to
all-or-nothing in 2020 Maze, but 2020 SPR has a borderline group with a
few fast words, which is where the step 6 cutoff matters.

## Candidate exclusion criteria: how many each would remove

The counts the default was chosen from: how many sessions each candidate
criterion would flag on its own. The base is sessions that pass steps 1–3
(complete, not a repeat participant, native English speaker); every count
is out of that base. Measures are over the critical trial (no practice).

```{r candidate-criteria}
# One logical column per criterion; NA where it doesn't apply to the task.
reading_only <- function(is_reading, flag) if_else(is_reading, flag, NA)
maze_only <- function(is_maze, flag) if_else(is_maze, flag, NA)
cloze_only <- function(task, flag) if_else(task == "cloze", flag, NA)
criteria <- sessions |>
  filter(!step_1_incomplete, !step_2_repeat, !step_3_not_native) |>
  mutate(
    no_trial = step_5_no_critical_trial,
    not_us = step_4_not_us,
    sliders_all_zero = sliders_all_zero,
    comprehension_wrong = reading_only(is_reading, !comprehension_correct),
    any_too_fast = reading_only(is_reading, no_trial | n_too_fast > 0),
    over_2_too_fast = reading_only(is_reading, no_trial | n_too_fast > 2),
    over_10pct_too_fast = reading_only(is_reading, no_trial | n_too_fast / words > .1),
    any_too_slow = reading_only(is_reading, no_trial | n_too_slow > 0),
    over_2_too_slow = reading_only(is_reading, no_trial | n_too_slow > 2),
    maze_accuracy_low = maze_only(is_maze, no_trial | !coalesce(maze_accuracy >= params$maze_accuracy_min, FALSE)),
    cloze_nonsense = cloze_only(task, step_8_cloze_nonsense)
  )
criterion_cols <- c("not_us", "sliders_all_zero", "comprehension_wrong", "any_too_fast", "over_2_too_fast",
                    "over_10pct_too_fast", "any_too_slow", "over_2_too_slow", "maze_accuracy_low",
                    "cloze_nonsense")
stopifnot(!anyNA(criteria$not_us), !anyNA(criteria$sliders_all_zero),
          # Every reading session has a value for every reading criterion.
          !anyNA(filter(criteria, is_reading)$any_too_fast))

criteria |>
  pivot_longer(all_of(criterion_cols), names_to = "criterion", values_to = "flagged") |>
  filter(!is.na(flagged)) |>
  group_by(criterion, study, task, round) |>
  summarize(cell = sprintf("%d (%.0f%%)", sum(flagged), 100 * mean(flagged)), .groups = "drop") |>
  mutate(criterion = factor(criterion, levels = criterion_cols),
         column = paste(study, task, round)) |>
  arrange(study, task, round) |>
  select(-study, -task, -round) |>
  pivot_wider(names_from = column, values_from = cell, values_fill = "–") |>
  arrange(criterion) |>
  show_table(paste0("Sessions flagged by each criterion on its own, n (% of base). ",
                    "RT window ", params$rt_min, "–", params$rt_max, " ms; Maze accuracy threshold ",
                    params$maze_accuracy_min, "; – = does not apply"))

criteria |>
  count(study, task, round, name = "base") |>
  pivot_wider(names_from = round, values_from = base) |>
  show_table("Base sessions (complete, not a repeat, native English speaker)")
```

Do the reading-task criteria pick out the same sessions? For each reading
session, how many of these four it fails: comprehension wrong, more than 2
words too fast, more than 2 words too slow, Maze accuracy low (Maze and
mazerace only, so SPR sessions can fail at most three).

```{r criteria-overlap, fig.height = 4, fig.width = 10}
overlap_cols <- c("comprehension_wrong", "over_2_too_fast", "over_2_too_slow", "maze_accuracy_low")
criteria_overlap <- criteria |>
  filter(is_reading) |>
  mutate(n_failed = rowSums(across(all_of(overlap_cols)), na.rm = TRUE),
         panel = paste(study, task))
ggplot(criteria_overlap, aes(x = round, fill = factor(n_failed))) +
  geom_bar(position = "fill") +
  facet_wrap(~panel, nrow = 1) +
  scale_fill_viridis_d(option = "magma", direction = -1, end = .9) +
  labs(x = NULL, y = "Proportion of base sessions", fill = "Criteria\nfailed",
       title = "Reading sessions: number of the four criteria failed")
```

The most common combinations of failed criteria (reading sessions,
pooled over rounds):

```{r criteria-combinations}
criteria_overlap |>
  filter(n_failed > 0) |>
  mutate(combination = pmap_chr(across(all_of(overlap_cols)), \(...) {
    flags <- c(...)
    paste(overlap_cols[coalesce(flags, FALSE)], collapse = " + ")
  })) |>
  count(study, task, combination) |>
  left_join(count(criteria_overlap, study, task, name = "base"), by = c("study", "task")) |>
  mutate(prop_of_base = round(n / base, 2)) |>
  select(-base) |>
  arrange(study, task, desc(n)) |>
  slice_head(n = 5, by = c(study, task)) |>
  show_table("Top 5 combinations of failed criteria per study and task (prop_of_base: share of that study x task's base sessions)")
```

# Session sets

All figures draw on one of these sets of sessions. The main figures use
**`r params$main_set`**; the robustness section compares all of them.

- **main**: the default exclusions above.
- **comprehension**: main, plus a correct comprehension answer (reading
  tasks).
- **strict_timing**: main, plus no word at all outside
  `r params$rt_min`–`r params$rt_max` ms in the critical trial (reading
  tasks).
- **high_attention**: the strictest set, for participants paying the most
  attention: main, plus comprehension *and* strict_timing (reading tasks),
  and, for every task, dropping sessions whose event sliders were all left
  at 0 (in main, those sessions keep their task data).
- **no_us_exclusion**: main without step 4 (citizenship/residence).
- **task_first**: main, restricted to sessions that did the critical task
  before the event sliders.
- **original**: each study's original pipeline rules
  (`excl_task_original`; `excl_expectations_original` for the sliders).

Cloze sessions are the same in main, comprehension and strict_timing; in
high_attention they differ from main only by the slider rule.
The event-expectation figures use the same sets (minus sessions with all
sliders at 0), except original, which uses each study's original slider
rule (`excl_expectations_original`).

```{r session-sets}
# The sets themselves are defined in analysis/analysis_data.R.
imap(session_sets, \(ids, set) count(filter(sessions, session_id %in% ids), study, round, task) |>
       mutate(set = set)) |>
  list_rbind() |>
  mutate(set = factor(set, levels = set_levels)) |>
  pivot_wider(names_from = set, values_from = n, values_fill = 0) |>
  arrange(study, task, round) |>
  show_table("Sessions in each set (task data), by study, task and round")
```

# Event expectations

Each participant moved three sliders (Democratic candidate, Republican
candidate, someone else); probabilities are each slider divided by their
sum. In 2020, a random half were asked about the vice presidency
(Harris vs. Pence) and half about the presidency (Biden vs. Trump).
The same exclusions apply as for the task data, so sessions that failed
their task's quality check (inattentive or not-good-faith participants)
are left out; see *Default exclusions*. Sessions with all sliders at 0 have
no probabilities and are left out too.

Grey symbols are what forecasters and betting markets said at the time
(`analysis/external_expectations.csv`, which records each value's source,
time window and how it was extracted): the point is the mean over the
round's collection window and the bar the range. In 2020 the
vice-presidency question has the same answer as the presidency question
(Harris is vice president exactly when Biden wins), so the same reference
values apply to both. After the election there are no forecasts; the
markets still gave Trump 6–12% after the 2020 race was called, while the
2024 market had already resolved for Trump before the post wave.

```{r expectations, fig.height = 3.5, fig.width = 9}
expectation_plot_data <- sessions |>
  filter(session_id %in% expectation_sets[[params$main_set]]) |>
  mutate(target = recode(expectation_target, vice_president = "vice president"),
         panel = paste(study, target))
external_expectations <- read_csv(here("analysis", "external_expectations.csv"),
                                  col_types = cols(study = col_character())) |>
  mutate(round = factor(round, levels = round_levels),
         # Drop the parenthesized list of markets from the legend label.
         source = str_remove(source, " \\(.*\\)"))
stopifnot(all(external_expectations$study %in% c("2020", "2024")),
          !anyNA(external_expectations$round),
          with(external_expectations, all(p_dem_low <= p_dem & p_dem <= p_dem_high)))
ggplot(expectation_plot_data, aes(x = round, y = expect_prob_dem, color = target, group = target)) +
  line_with_errorbars(dodge) +
  geom_pointrange(data = external_expectations,
                  mapping = aes(x = round, y = p_dem, ymin = p_dem_low, ymax = p_dem_high, shape = source),
                  inherit.aes = FALSE, color = "grey45", position = position_nudge(x = .25)) +
  facet_wrap(~study) +
  scale_color_brewer(palette = "Dark2") +
  scale_shape_manual(values = c(17, 15, 18)) +
  coord_cartesian(ylim = c(0, 1)) +
  labs(x = NULL, y = "P(Democratic candidate wins)", color = "Participants asked about", shape = "At the time",
       title = "Expected probability that the Democratic candidate wins")
```

```{r expectations-dist, fig.height = 3.5}
ggplot(expectation_plot_data, aes(x = expect_prob_dem, fill = round)) +
  geom_histogram(binwidth = .05, position = "identity", alpha = .5) +
  facet_wrap(~panel, scales = "free_y", nrow = 1) +
  scale_fill_brewer(palette = "Dark2") +
  labs(x = "P(Democratic candidate wins)", y = "Sessions", fill = NULL)
```

National polling averages at the time (538; vote shares, not
probabilities, so not plotted): 2020 pre, Biden 52.1% vs. Trump 43.0%
(Oct 30) and 51.8% vs. 43.4% (Nov 3); 2024 pre, Harris 47.9% vs. Trump 46.8%
(Oct 31). Sources: archived `presidential_poll_averages_2020.csv` and
`presidential_general_averages.csv` from projects.fivethirtyeight.com
(Wayback Machine).

# Cloze completions

Each session contributes one completion, so proportions are over
sessions. Two views (columns described in `DATA.md`):

- **First target pronoun**: among completions with at least one pronoun
  referring to the target office-holder (2020: the vice president; 2024:
  the president), which kind comes first (`first_coref_pronoun`).
- **References anywhere**: the share of completions containing each kind of
  reference, anywhere in the completion; one completion can count in
  several categories.

```{r cloze, fig.height = 4}
cloze_levels <- c("she", "he", "they", "hedged", "female_candidate_name", "male_candidate_name",
                  "other_candidate_name", "target_office_np", "other_office_np", "generic_np", "other", "blank")
pronoun_codes <- c("she", "he", "they", "hedged")
pronoun_code_scale <- scale_color_manual(values = c(pronoun_colors, hedged = "grey40"),
                                         breaks = c(names(pronoun_colors), "hedged"))

# One row per session x code: 1 if the session's completion has that code.
code_indicators <- function(cloze_df, code_column) {
  cloze_df |>
    mutate(code = factor(.data[[code_column]], levels = cloze_levels)) |>
    select(study, round, session_id, code) |>
    mutate(present = 1) |>
    complete(nesting(study, round, session_id), code, fill = list(present = 0))
}
# Completions with a target-office pronoun only: 1 if it is the first one.
first_pronoun_indicators <- function(cloze_df) {
  cloze_df |>
    filter(first_coref_pronoun != "none") |>
    mutate(code = factor(first_coref_pronoun, levels = pronoun_codes)) |>
    select(study, round, session_id, code) |>
    mutate(present = 1) |>
    complete(nesting(study, round, session_id), code, fill = list(present = 0))
}
cloze_kept <- filter(cloze, session_id %in% kept_sessions)
stopifnot(!anyNA(factor(cloze_kept$cloze_code, levels = cloze_levels)),
          all(cloze_kept$first_coref_pronoun %in% c(pronoun_codes, "none")))
first_pronouns <- first_pronoun_indicators(cloze_kept)
stopifnot(all(count(first_pronouns, session_id)$n == length(pronoun_codes)))

cloze_kept |>
  summarize(completions = n(), with_target_pronoun = sum(first_coref_pronoun != "none"), .by = c(study, round)) |>
  arrange(study, round) |>
  show_table("Completions with at least one pronoun referring to the target office-holder")

ggplot(first_pronouns, aes(x = round, y = present, color = code, group = code)) +
  line_with_errorbars(dodge) +
  facet_wrap(~study) +
  pronoun_code_scale +
  labs(x = NULL, y = "Proportion of completions with a target pronoun", color = "First target pronoun",
       title = "Cloze: first pronoun referring to the target office-holder")
```

```{r cloze-anywhere, fig.height = 4}
# Each kind of reference, anywhere in the completion (repeats allowed).
reference_columns <- c(
  "she (target)" = "coref_she", "he (target)" = "coref_he", "they (target)" = "coref_they",
  "hedged (target)" = "coref_hedge",
  "Harris" = "has_female_candidate_name", "male candidate (target office)" = "has_male_candidate_name",
  "target office NP" = "has_target_office_np",
  "other-office candidate (2020: Biden, Trump)" = "has_other_candidate_name",
  "other office NP" = "has_other_office_np", "pronoun for other office-holder" = "any_coref_other",
  "generic NP (winner, candidate)" = "has_generic_np"
)
references_anywhere <- cloze_kept |>
  mutate(any_coref_other = coref_other_she | coref_other_he | coref_other_they | coref_other_hedge) |>
  select(study, round, session_id, all_of(reference_columns)) |>
  pivot_longer(-c(study, round, session_id), names_to = "reference", values_to = "present") |>
  mutate(reference = factor(reference, levels = names(reference_columns)), present = as.numeric(present))
stopifnot(!anyNA(references_anywhere$present))

ggplot(filter(references_anywhere, str_detect(reference, "\\(target\\)$")),
       aes(x = round, y = present, color = str_remove(reference, " \\(target\\)"),
           group = reference)) +
  line_with_errorbars(dodge) +
  facet_wrap(~study) +
  pronoun_code_scale +
  labs(x = NULL, y = "Proportion of completions", color = "Pronoun",
       title = "Cloze: completions containing a pronoun for the target office-holder")
ggplot(filter(references_anywhere, !str_detect(reference, "\\(target\\)$")),
       aes(x = round, y = present, color = reference, group = reference)) +
  line_with_errorbars(dodge) +
  facet_wrap(~study) +
  scale_color_brewer(palette = "Dark2") +
  labs(x = NULL, y = "Proportion of completions", color = NULL,
       title = "Cloze: completions containing other references")
```

The first referring expression of any kind (`cloze_code`), for reference:

```{r cloze-table}
cloze_kept |>
  count(study, round, cloze_code) |>
  pivot_wider(names_from = c(study, round), values_from = n, values_fill = 0) |>
  show_table("Cloze completion counts (first reference)")
```

## Original vs. shared cloze coding

Each study's original pipeline coded the completions its own way
(`cloze_code_original`). The shared code (`cloze_code`) applies one rule to
both: **the first referring expression in the completion**. The table maps
each original label to the shared category it corresponds to, then counts
how often the two agree.

How the originals differ from the shared rule:

- **Name vs. pronoun precedence.** When a completion has both, 2020's
  original took the name, 2024's took the pronoun; the shared code takes
  whichever comes first.
- **Office noun phrases.** 2020's original had no category for "the vice
  president will…" (it was `none`); 2024 called it `ambiguous NP`. The
  shared code splits these by office: `target_office_np` (the office the
  item is about), `other_office_np` (the other office) and `generic_np`
  ("the winner").
- **Hedges.** 2020's original `both` and 2024's `hedged` correspond to the
  shared `hedged`.
- **2024 "them" bug.** The 2024 original meant to skip "them" when it refers
  back to the plural in item 9's prompt ("…many challenges, and one of"),
  but tested the response instead of the prompt, so those completions were
  coded as singular *they*.

```{r cloze-original-mapping}
original_to_shared <- tribble(
  ~study, ~cloze_code_original, ~original_as_shared,
  "2020", "female", "she",
  "2020", "male", "he",
  "2020", "neutral", "they",
  "2020", "both", "hedged",
  "2020", "harris", "female_candidate_name",
  "2020", "pence", "male_candidate_name",
  "2020", "biden", "other_candidate_name",
  "2020", "trump", "other_candidate_name",
  "2020", "none", "other",
  "2024", "pronoun female", "she",
  "2024", "pronoun male", "he",
  "2024", "pronoun neutral", "they",
  "2024", "hedged", "hedged",
  "2024", "Harris", "female_candidate_name",
  "2024", "Trump", "male_candidate_name",
  "2024", "ambiguous NP", "target_office_np",
  "2024", "OTHER", "other"
)
cloze_original <- map(c("2020", "2024"), \(s) read_study(s, "cloze") |> mutate(study = s)) |>
  list_rbind() |>
  select(study, session_id, cloze_item, prompt, response, cloze_code_original, cloze_code) |>
  # Blank completions have no original code; both codings agree they are blank.
  left_join(original_to_shared, by = c("study", "cloze_code_original"), relationship = "many-to-one") |>
  mutate(original_as_shared = if_else(is.na(cloze_code_original), "blank", original_as_shared),
         round = factor(str_extract(session_id, "pre|post"), levels = round_levels))
stopifnot(!anyNA(cloze_original$original_as_shared),
          setequal(cloze_original$session_id, cloze$session_id))
cloze_original <- filter(cloze_original, session_id %in% kept_sessions)

cloze_original |>
  count(study, original = cloze_code_original, shared = cloze_code,
        agree = original_as_shared == cloze_code) |>
  arrange(study, agree, desc(n)) |>
  show_table("Original vs. shared coding (kept sessions); agree = the original label maps to the shared category")
```

Examples of each kind of disagreement (up to 3 random completions per
cell; the end of the prompt is shown for context):

```{r cloze-disagreement-examples}
set.seed(2020)
cloze_original |>
  filter(original_as_shared != cloze_code) |>
  group_by(study, cloze_code_original, cloze_code) |>
  slice_sample(n = 3) |>
  ungroup() |>
  transmute(study, original = cloze_code_original, shared = cloze_code, item = cloze_item,
            prompt_end = paste0("…", str_sub(prompt, -40)), response) |>
  arrange(study, original, shared) |>
  show_table("Disagreements between original and shared cloze coding")
```

What the choice does to the pronoun proportions:

```{r cloze-coding-comparison, fig.height = 4}
bind_rows(
  shared = code_indicators(cloze_original, "cloze_code"),
  original = code_indicators(cloze_original, "original_as_shared"),
  .id = "coding"
) |>
  filter(code %in% pronoun_codes) |>
  ggplot(aes(x = round, y = present, color = code, linetype = coding,
             group = interaction(code, coding))) +
  line_with_errorbars(position_dodge(width = .3)) +
  facet_wrap(~study) +
  pronoun_code_scale +
  labs(x = NULL, y = "Proportion of completions", color = "First reference", linetype = "Coding",
       title = "Cloze pronoun proportions under the original and the shared coding")
```

# Reading times

```{r reading-prep}
critical <- critical_words |>
  filter(session_id %in% kept_sessions)
# Missing RTs (2020 SPR logged a few as None) count as outside the window.
in_window <- coalesce(critical$rt >= params$rt_min & critical$rt <= params$rt_max, FALSE)
maze_ok <- !params$maze_correct_only | critical$task == "spr" | coalesce(critical$maze_correct, FALSE)
critical |>
  mutate(removed = !(in_window & maze_ok)) |>
  group_by(study, task) |>
  summarize(words = n(), prop_removed = round(mean(removed), 3), .groups = "drop") |>
  show_table("Critical-trial words removed by the RT window / Maze accuracy filter")
critical_rt <- critical[in_window & maze_ok, ]
```

RTs are plotted on a log scale, so means and CIs are computed on log RT
(geometric means), which down-weights long RTs.

```{r rt-helpers}
# The log10 transform applies before stat_summary, so means are geometric means.
log_ms_axis <- scale_y_log10(name = "RT (ms, geometric mean)")

# Words in the given critical sentence, positioned relative to its pronoun.
relative_to_pronoun <- function(df, sentence, pronoun_flag) {
  pronoun_position <- df |>
    filter(sentence_index == sentence, .data[[pronoun_flag]]) |>
    select(session_id, pronoun_word = word_index_in_sentence)
  df |>
    filter(sentence_index == sentence) |>
    inner_join(pronoun_position, by = "session_id", relationship = "many-to-one") |>
    mutate(position = word_index_in_sentence - pronoun_word)
}

# Sentences differ in length and pronoun position, so far-out positions come
# from only some items. Keep positions present in at least half the sessions
# of each study x task.
well_covered_positions <- function(df) {
  df |>
    group_by(study, task) |>
    mutate(sessions = n_distinct(session_id)) |>
    group_by(study, task, position) |>
    filter(n_distinct(session_id) >= sessions / 2) |>
    ungroup() |>
    select(-sessions)
}

# Region words, relative to the pronoun: Maze, the pronoun itself; SPR, the
# pronoun and the next three words (spillover), each kept as its own word
# (not averaged) so the spillover positions can be compared.
region_positions <- list(maze = 0, spr = 0:3)
region_words <- function(df) {
  stopifnot(all(df$task %in% names(region_positions)))
  df |>
    filter(map2_lgl(task, position, \(tk, pos) pos %in% region_positions[[tk]])) |>
    mutate(word = factor(if_else(position == 0, "pronoun", paste0("pronoun +", position)),
                         levels = c("pronoun", paste0("pronoun +", 1:3))))
}

pronoun_2_pairs <- function(df) {
  mutate(df, pair = if_else(pro1_type == pro2_type, "match", "mismatch"))
}

reading_tasks <- c("maze", "spr")
s1 <- critical_rt |>
  filter(task %in% reading_tasks) |>
  relative_to_pronoun(1, "is_pro1")
s2 <- critical_rt |>
  filter(task %in% reading_tasks) |>
  relative_to_pronoun(2, "is_pro2") |>
  pronoun_2_pairs()
```

## Time courses

Whole critical sentences, aligned on the pronoun (0), in the
**`r params$main_set`** set. Positions
are kept if at least half the sessions of that study and task have them.
Pronoun 2 either matches pronoun 1 (he-he, she-she, they-they) or switches
gender (he-she, she-he).

```{r time-course-functions}
plot_time_course_1 <- function(df, title) {
  ggplot(well_covered_positions(df), aes(x = position, y = rt, color = pro1_type, group = pro1_type)) +
    line_with_errorbars(dodge) +
    geom_vline(xintercept = 0, color = "grey70") +
    facet_grid(paste(study, task) ~ round, scales = "free") +
    pronoun_scale +
    log_ms_axis +
    labs(x = "Word position relative to pronoun 1", color = "Pronoun 1", title = title)
}
plot_time_course_2 <- function(df, title) {
  ggplot(well_covered_positions(df),
         aes(x = position, y = rt, color = pro2_type, linetype = pair, group = interaction(pro2_type, pair))) +
    line_with_errorbars(dodge) +
    geom_vline(xintercept = 0, color = "grey70") +
    facet_grid(paste(study, task) ~ round, scales = "free") +
    pronoun_scale +
    log_ms_axis +
    labs(x = "Word position relative to pronoun 2", color = "Pronoun 2", linetype = "Pronoun pair",
         title = title)
}
```

```{r time-course-1, fig.height = 8, fig.width = 11}
plot_time_course_1(s1, paste0("Sentence 1 (", params$main_set, " set)"))
```

```{r time-course-2, fig.height = 8, fig.width = 11}
plot_time_course_2(s2, paste0("Sentence 2 (", params$main_set, " set)"))
```

## Analysis region

Maze: RT at the pronoun. SPR: the pronoun and each of the next three words
(spillover), shown separately. Values are per word, after the RT window
(and, for Maze, the first-try accuracy filter).

```{r region-data}
region_1 <- region_words(s1)
region_2 <- region_words(s2)
```

```{r rt-pronoun-1-maze, fig.height = 3.5, fig.width = 6}
ggplot(filter(region_1, task == "maze"), aes(x = round, y = rt, color = pro1_type, group = pro1_type)) +
  line_with_errorbars(dodge) +
  facet_wrap(~study, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 1", title = "Maze: RT at pronoun 1")
```

```{r rt-pronoun-1-spr, fig.height = 5, fig.width = 10}
ggplot(filter(region_1, task == "spr"), aes(x = round, y = rt, color = pro1_type, group = pro1_type)) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ word, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 1", title = "SPR: RT at pronoun 1 and the next three words")
```

```{r rt-pronoun-2-maze, fig.height = 3.5, fig.width = 6}
ggplot(filter(region_2, task == "maze"), aes(x = round, y = rt, color = pro2_type,
                                             linetype = pair, group = interaction(pro2_type, pair))) +
  line_with_errorbars(dodge) +
  facet_wrap(~study, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 2", linetype = "Pronoun pair", title = "Maze: RT at pronoun 2")
```

```{r rt-pronoun-2-spr, fig.height = 5, fig.width = 10}
ggplot(filter(region_2, task == "spr"), aes(x = round, y = rt, color = pro2_type,
                                            linetype = pair, group = interaction(pro2_type, pair))) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ word, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 2", linetype = "Pronoun pair",
       title = "SPR: RT at pronoun 2 and the next three words")
```

## Maze accuracy at the pronoun

Proportion of sessions choosing the pronoun correctly on the first try
(all words, no RT window), in the **`r params$main_set`** set.

```{r maze-pronoun-accuracy, fig.height = 3.5, fig.width = 10}
maze_pronoun_words <- critical_words |>
  filter(task == "maze", is_pro1 | is_pro2) |>
  pronoun_2_pairs() |>
  mutate(pronoun = if_else(is_pro1, "pronoun 1", "pronoun 2"),
         pronoun_type = if_else(is_pro1, pro1_type, pro2_type),
         # Pronoun 1 is preceded only by sentence 1, so the pair is irrelevant there.
         pair = if_else(is_pro1, "(sentence 1)", pair))
ggplot(filter(maze_pronoun_words, session_id %in% kept_sessions), aes(x = round, y = as.numeric(maze_correct), color = pronoun_type,
                                  linetype = pair, group = interaction(pronoun_type, pair))) +
  line_with_errorbars(dodge) +
  facet_wrap(~ paste(study, pronoun), nrow = 1) +
  pronoun_scale +
  labs(x = NULL, y = "Proportion correct on first try", color = "Pronoun", linetype = "Pronoun pair",
       title = "Maze: accuracy on the pronoun")
```

## Mazerace (2020 only)

The context sentence is followed by "The vice president will be (a)
black/white/Black/White (person) …".

```{r mazerace, fig.height = 3.5}
race <- critical_rt |>
  filter(task == "mazerace", is_race_adjective) |>
  mutate(race = tolower(race_adjective),
         capitalized = if_else(race_adjective == str_to_title(race_adjective), "Capitalized", "lowercase"))
ggplot(race, aes(x = round, y = rt, color = race, linetype = capitalized,
                 group = interaction(race, capitalized))) +
  line_with_errorbars(dodge) +
  scale_color_brewer(palette = "Dark2") +
  log_ms_axis +
  labs(x = NULL, color = "Adjective", linetype = NULL, title = "Mazerace: RT at the race adjective")
```

# Recall

After the reading task, participants said whom the writer believed would win.

Split by the pronoun pair the participant read (pronoun 1 – pronoun 2).

```{r recall, fig.height = 4.5, fig.width = 9}
pair_levels <- c("he–he", "she–she", "they–they", "he–she", "she–he")
recall_by_pronoun <- recall |>
  filter(session_id %in% kept_sessions) |>
  inner_join(distinct(filter(critical_words, task %in% reading_tasks), session_id, pro1_type, pro2_type),
             by = "session_id", relationship = "one-to-one") |>
  mutate(round = factor(round, levels = round_levels), study = as.character(study),
         pronoun_pair = factor(paste0(pro1_type, "–", pro2_type), levels = pair_levels))
stopifnot(!anyNA(recall_by_pronoun$pronoun_pair))
plot_recall <- function(df, facet, title = NULL) {
  df |>
    count(study, round, across(any_of("party")), pronoun_pair, recall_response) |>
    mutate(prop = n / sum(n), .by = c(study, round, any_of("party"), pronoun_pair)) |>
    mutate(recall_response = factor(recall_response, levels = names(recall_colors))) |>
    ggplot(aes(x = pronoun_pair, y = prop, fill = recall_response)) +
    geom_col() +
    facet +
    scale_fill_manual(values = recall_colors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(x = "Pronoun 1 – pronoun 2", y = "Proportion of sessions", fill = "Writer believes...", title = title)
}
plot_recall(recall_by_pronoun, facet_grid(study ~ round))
```

# Participants

```{r demographics}
sessions |>
  filter(session_id %in% kept_sessions) |>
  group_by(study, round) |>
  summarize(
    n = n(),
    age_median = median(age, na.rm = TRUE),
    female = mean(gender == "Female", na.rm = TRUE),
    democrat = mean(political_affiliation == "Democrat", na.rm = TRUE),
    republican = mean(political_affiliation == "Republican", na.rm = TRUE),
    prefer_dem = mean(election_pref %in% c("Kamala Harris", "Joe Biden"), na.rm = TRUE),
    prefer_rep = mean(election_pref %in% c("Donald Trump", "Mike Pence"), na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(across(female:prefer_rep, \(x) round(x, 2))) |>
  show_table("Kept sessions: demographics (proportions)")
```

```{r awareness}
sessions |>
  filter(session_id %in% kept_sessions, study == "2020", round == "post") |>
  count(aware) |>
  mutate(prop = round(n / sum(n), 2)) |>
  show_table("2020 post-election: aware the race had been called?")
```

# By expected probability that the female candidate wins

Each session's own event expectation, P(female candidate wins), against its
critical-trial result, in the **`r params$main_set`** set. Harris is the
Democratic candidate in both studies, so this is `expect_prob_dem`. In 2020
the vice-presidency and presidency questions are pooled: Harris becomes vice
president exactly when Biden wins. Sessions with all sliders at 0 have no
expectation and are left out. Lines are per-session fits with 95% CIs:
linear on log RT for RTs, logistic for cloze proportions. Dots are sessions
(cloze: one dot per session per pronoun, at 0 or 1 with a little vertical
jitter).

```{r p-female-setup}
p_female <- sessions |>
  filter(!is.na(expect_prob_dem)) |>
  select(session_id, p_female = expect_prob_dem)
with_p_female <- function(df) inner_join(df, p_female, by = "session_id", relationship = "many-to-one")
p_female_axis <- scale_x_continuous(name = "P(female candidate wins), participant's own estimate",
                                    limits = c(0, 1), breaks = c(0, .5, 1))
```

```{r p-female-cloze, fig.height = 5, fig.width = 9}
# Denominator: completions with a target pronoun (including hedged ones,
# which are not plotted).
first_pronouns |>
  with_p_female() |>
  filter(code %in% names(pronoun_colors)) |>
  ggplot(aes(x = p_female, y = present, color = code, fill = code)) +
  geom_smooth(method = "glm", method.args = list(family = binomial), formula = y ~ x, alpha = .15) +
  # Outcomes are 0/1; a little vertical jitter shows how many sessions sit at each x.
  geom_point(position = position_jitter(width = 0, height = .03, seed = 1), alpha = .2, size = .8) +
  facet_grid(study ~ round) +
  pronoun_scale +
  scale_fill_manual(values = pronoun_colors, guide = "none") +
  p_female_axis +
  coord_cartesian(ylim = c(0, 1)) +
  labs(y = "Proportion of completions with a target pronoun", color = "First target pronoun",
       title = "Cloze: first target pronoun by expected P(female candidate wins)")
```

```{r p-female-maze, fig.height = 5, fig.width = 9}
ggplot(with_p_female(filter(region_1, task == "maze")),
       aes(x = p_female, y = rt, color = pro1_type, fill = pro1_type)) +
  geom_point(alpha = .2, size = .8) +
  geom_smooth(method = "lm", formula = y ~ x, alpha = .15) +
  facet_grid(study ~ round) +
  pronoun_scale +
  scale_fill_manual(values = pronoun_colors, guide = "none") +
  p_female_axis +
  log_ms_axis +
  labs(color = "Pronoun 1", title = "Maze: RT at pronoun 1 by expected P(female candidate wins)")
```

```{r p-female-spr, fig.height = 9, fig.width = 11}
ggplot(with_p_female(filter(region_1, task == "spr")),
       aes(x = p_female, y = rt, color = pro1_type, fill = pro1_type)) +
  geom_point(alpha = .2, size = .8) +
  geom_smooth(method = "lm", formula = y ~ x, alpha = .15) +
  facet_grid(study + round ~ word) +
  pronoun_scale +
  scale_fill_manual(values = pronoun_colors, guide = "none") +
  p_female_axis +
  log_ms_axis +
  labs(color = "Pronoun 1",
       title = "SPR: RT at pronoun 1 and the next three words by expected P(female candidate wins)")
```

# By political affiliation

The same summaries split by self-reported party affiliation, in the
**`r params$main_set`** set. "Other / none / didn't say" pools "Other",
"None", "Rather not say" and missing answers.

```{r party-setup}
party_levels <- c("Democrat", "Republican", "Independent", "other / none / didn't say")
party <- sessions |>
  transmute(session_id,
            party = factor(if_else(political_affiliation %in% party_levels[1:3], political_affiliation,
                                   party_levels[4]), levels = party_levels))
stopifnot(!anyNA(party$party))
with_party <- function(df) inner_join(df, party, by = "session_id", relationship = "many-to-one")
sessions |>
  filter(session_id %in% kept_sessions) |>
  with_party() |>
  count(study, round, party) |>
  pivot_wider(names_from = party, values_from = n, values_fill = 0) |>
  show_table("Sessions per party affiliation")
```

```{r party-expectations, fig.height = 3.5, fig.width = 10}
expectation_plot_data |>
  with_party() |>
  ggplot(aes(x = round, y = expect_prob_dem, color = party, group = party)) +
  line_with_errorbars(dodge) +
  facet_wrap(~study) +
  scale_color_brewer(palette = "Set1") +
  coord_cartesian(ylim = c(0, 1)) +
  labs(x = NULL, y = "P(Democratic candidate wins)", color = NULL,
       title = "Expected probability that the Democratic candidate wins, by party")
```

```{r party-cloze, fig.height = 5, fig.width = 11}
first_pronouns |>
  with_party() |>
  ggplot(aes(x = round, y = present, color = code, group = code)) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ party) +
  pronoun_code_scale +
  labs(x = NULL, y = "Proportion of completions with a target pronoun", color = "First target pronoun",
       title = "Cloze: first pronoun referring to the target office-holder, by party")
```

```{r party-maze, fig.height = 5, fig.width = 11}
ggplot(with_party(filter(region_1, task == "maze")), aes(x = round, y = rt, color = pro1_type, group = pro1_type)) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ party, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 1", title = "Maze: RT at pronoun 1, by party")
ggplot(with_party(filter(region_2, task == "maze")), aes(x = round, y = rt, color = pro2_type, linetype = pair,
                                                         group = interaction(pro2_type, pair))) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ party, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 2", linetype = "Pronoun pair", title = "Maze: RT at pronoun 2, by party")
```

```{r party-spr, fig.height = 12, fig.width = 11}
ggplot(with_party(filter(region_1, task == "spr")), aes(x = round, y = rt, color = pro1_type, group = pro1_type)) +
  line_with_errorbars(dodge) +
  facet_grid(paste(study, word) ~ party, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 1", title = "SPR: RT at pronoun 1 and the next three words, by party")
ggplot(with_party(filter(region_2, task == "spr")), aes(x = round, y = rt, color = pro2_type, linetype = pair,
                                                        group = interaction(pro2_type, pair))) +
  line_with_errorbars(dodge) +
  facet_grid(paste(study, word) ~ party, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 2", linetype = "Pronoun pair",
       title = "SPR: RT at pronoun 2 and the next three words, by party")
```

```{r party-recall, fig.height = 8, fig.width = 11}
recall_by_pronoun |>
  with_party() |>
  plot_recall(facet_grid(paste(study, round) ~ party), title = "Recall, by party")
```

# Robustness: the same summaries in every session set

Each panel column is one session set. The RT window and Maze filter are the
same in every set.

```{r robustness-data}
in_set <- function(df, set) filter(df, session_id %in% session_sets[[set]]) |> mutate(set = set)
across_sets <- function(df) {
  map(set_levels, \(set) in_set(df, set)) |>
    list_rbind() |>
    mutate(set = factor(set, levels = set_levels))
}
# Same RT window and Maze filter as above, but before restricting to the main set.
all_rt <- critical_words |>
  filter(task %in% reading_tasks,
         coalesce(rt >= params$rt_min & rt <= params$rt_max, FALSE),
         !params$maze_correct_only | task == "spr" | coalesce(maze_correct, FALSE))
pronoun_1_all_sets <- all_rt |>
  relative_to_pronoun(1, "is_pro1") |>
  region_words() |>
  across_sets()
pronoun_2_all_sets <- all_rt |>
  relative_to_pronoun(2, "is_pro2") |>
  pronoun_2_pairs() |>
  region_words() |>
  across_sets()
cloze_all_sets <- first_pronoun_indicators(cloze) |>
  across_sets()
```

```{r robustness-pronoun-1-maze, fig.height = 4.5, fig.width = 12}
ggplot(filter(pronoun_1_all_sets, task == "maze"), aes(x = round, y = rt, color = pro1_type, group = pro1_type)) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ set, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 1", title = "Maze: RT at pronoun 1, by session set")
```

```{r robustness-pronoun-1-spr, fig.height = 12, fig.width = 12}
ggplot(filter(pronoun_1_all_sets, task == "spr"), aes(x = round, y = rt, color = pro1_type, group = pro1_type)) +
  line_with_errorbars(dodge) +
  facet_grid(paste(study, word) ~ set, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 1", title = "SPR: RT at pronoun 1 and the next three words, by session set")
```

```{r robustness-pronoun-2-maze, fig.height = 4.5, fig.width = 12}
ggplot(filter(pronoun_2_all_sets, task == "maze"), aes(x = round, y = rt, color = pro2_type, linetype = pair,
                                                       group = interaction(pro2_type, pair))) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ set, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 2", linetype = "Pronoun pair", title = "Maze: RT at pronoun 2, by session set")
```

```{r robustness-pronoun-2-spr, fig.height = 12, fig.width = 12}
ggplot(filter(pronoun_2_all_sets, task == "spr"), aes(x = round, y = rt, color = pro2_type, linetype = pair,
                                                      group = interaction(pro2_type, pair))) +
  line_with_errorbars(dodge) +
  facet_grid(paste(study, word) ~ set, scales = "free_y") +
  pronoun_scale +
  log_ms_axis +
  labs(x = NULL, color = "Pronoun 2", linetype = "Pronoun pair",
       title = "SPR: RT at pronoun 2 and the next three words, by session set")
```

```{r robustness-cloze, fig.height = 4.5, fig.width = 12}
ggplot(cloze_all_sets, aes(x = round, y = present, color = code, group = code)) +
  line_with_errorbars(dodge) +
  facet_grid(study ~ set) +
  pronoun_code_scale +
  labs(x = NULL, y = "Proportion of completions with a target pronoun", color = "First target pronoun",
       title = "Cloze: first target pronoun, by session set (comprehension, strict_timing = main for cloze)")
```

```{r robustness-expectations, fig.height = 3.5, fig.width = 12}
imap(expectation_sets, \(ids, set) filter(sessions, session_id %in% ids) |> mutate(set = set)) |>
  list_rbind() |>
  mutate(set = factor(set, levels = set_levels),
         target = recode(expectation_target, vice_president = "vice president"),
         panel = paste(study, target)) |>
  ggplot(aes(x = round, y = expect_prob_dem, color = panel, group = panel)) +
  line_with_errorbars(dodge) +
  facet_wrap(~set, nrow = 1) +
  scale_color_brewer(palette = "Dark2") +
  coord_cartesian(ylim = c(0, 1)) +
  labs(x = NULL, y = "P(Democratic candidate wins)", color = NULL,
       title = "Event expectations, by session set")
```

Task order also matters for the event sliders: if the critical task primes
expectations, the task-first sessions are the cleaner measure.

```{r order-expectations, fig.height = 3.5}
ggplot(expectation_plot_data, aes(x = round, y = expect_prob_dem, color = task_order,
                                  group = task_order)) +
  line_with_errorbars(dodge) +
  facet_wrap(~panel, nrow = 1) +
  scale_color_brewer(palette = "Dark2") +
  coord_cartesian(ylim = c(0, 1)) +
  labs(x = NULL, y = "P(Democratic candidate wins)", color = NULL,
       title = "Event expectations by task order")
```

## Still to add

- Log vs. raw RT, and residualized RT (deferred to the modeling stage).
